---
title: "TPDstat Tutorial 8: Bootstrapping"
tutorial:
  id: "08-bootstrap"
output:
  learnr::tutorial:
    progressive: true
    ace_theme: github
    css: "css/tutorial.css"
    df_print: tibble
runtime: shiny_prerendered
description: "This tutorial will introduce you to bootstrapping."
---

<!-- Add JavaScript code for making the exercise code larger -->
<script language="JavaScript" src="js/exercise-font-size.js"></script>
 

```{r setup, include=FALSE}
# file.path(find.package('TPDtutor'), 'tutorials', 'tutorial.css')
library(gradethis)
library(learnr)
library(ggplot2)
library(dplyr)
library(TPDtutor)
library(tidyverse)
library(TPDdata)
library(infer)

tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = TRUE)
tut_reptitle <- "TPDstat Tutorial 7: Output Report"

library(gapminder)
```

## `infer` package

### Using `infer`

The `infer` package is a package that provides a unified interface for statistical inference tasks like calculating confidence intervals or performing hypothesis tests. The package comes with a sample of 500 entries from the General Social Survey (GSS), a long-running survey about American society and opinions. This data is loaded into your environment as `gss`.

The first step in using infer is to pass the data to the `specify()` function to tell `infer` what your dependent and independent variables are. If we are just calculating the mean or proportion of one variable, we just have a dependent variable. For instance, if we wanted to specify the `gss` variable `age` as our response variable, we would type:

```{r}
gss |>
  specify(response = age)
```

By itself this just selects this variable from the `gss` data and prepares it for the next steps.

### Exercises

Now you try to specify `hours` (number of hours worked in week before survey) as the response variable:

```{r gss-hours, exercise = TRUE}

```

```{r gss-hours-solution}
gss |>
  specify(response = hours) 
```

```{r gss-hours-check}
gradethis::grade_this_code()
```

### Generating bootstrap replications

Once you have specified the response variable, `infer` can generate repeated samples with replacement from the data using the `generate()` function. These are the bootstrap samples. The code for this looks like:

```{r}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap")
```

Here we are explicitly stating that we want the bootstrap, but omitting the `type` argument in this case will still produce a bootstrap. You can think of this as similar to the `rep_slice_sample()` function with `replace = TRUE`. Now try to add this step to your own code for the `hours` variable using 100 repeated samples.

```{r gss-genex, exercise = TRUE}
gss |>
  specify(response = hours) 
```

```{r gss-genex-solution}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap")
```

```{r gss-genex-check}
gradethis::grade_this_code()
```

### Calculating the summary statistics across bootstrap samples

Next we can use the `calculate()` function to calculate a summary statistic in each of the repeated samples. This will basically recreate the `group_by` and `summarize` steps of a `dplyr` chain, but will prepare the result for easily obtaining confidence intervals. To implement this, use the following code:

```{r}
gss |>
  specify(response = age) |>
  generate(reps = 100, type = "bootstrap") |>
  calculate(stat = "mean")
```

The `stat` argument specifies what type of statistics we are calculating and ca take on values like `"diff in means"`, and so on. Here we are interested in the mean. 

Now, you try to perform these calculations for the `hours` variable:

```{r gss-hours, exercise = TRUE}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap")
```

```{r gss-hours-solution}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap") |>
  calculate(stat = "mean")
```

```{r gss-hours-check}
gradethis::grade_this_code()
```

### Calculating confidence intervals

Finally, you can get a confidence interval from the `infer` package by passing this whole chain to the `get_confidence_interval()` function:

```{r}
gss |>
  specify(response = age) |>
  generate(reps = 100, type="bootstrap") |>
  calculate(stat = "mean") |>
  get_confidence_interval(level = 0.95)
```

We explicitly are asking for a 95% confidence interval, but if we wanted a 90% confidence interval, we could specify `level = 0.9`.

Now, you try! Finish your code here to get a 95% confidence interval for the mean of `hours`:

```{r gss-ci, exercise = TRUE}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap") |>
  calculate(stat = "mean")
```

```{r gss-ci-solution}
gss |>
  specify(response = hours) |>
  generate(reps = 100, type = "bootstrap") |>
  calculate(stat = "mean")
  get_confidence_interval(level = 0.95)
```

```{r gss-ci-check}
gradethis::grade_this_code()
```

## Submit

```{r context="setup", echo = FALSE}
TPDtutor::submission_ui
```

```{r context="server", echo = FALSE}
TPDtutor::submission_server()
```
