---
title: "TPDstat Tutorial 8: Bootstrapping"
tutorial:
  id: "08-bootstrap"
output:
  learnr::tutorial:
    progressive: true
    ace_theme: github
    css: "css/tutorial.css"
    df_print: tibble
runtime: shiny_prerendered
description: "This tutorial will introduce you to bootstrapping."
---

<!-- Add JavaScript code for making the exercise code larger -->
<script language="JavaScript" src="js/exercise-font-size.js"></script>
 

```{r setup, include=FALSE}
# file.path(find.package('TPDtutor'), 'tutorials', 'tutorial.css')
library(gradethis)
library(learnr)
library(ggplot2)
library(dplyr)
library(TPDtutor)
library(tidyverse)
library(TPDdata)
library(infer)

tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = TRUE)
tut_reptitle <- "TPDstat Tutorial 7: Output Report"

library(gapminder)
```

## `infer` package

### Using `infer`

The `infer` package is a package that provides a unified interface for statistical inference tasks like calculating confidence intervals or performing hypothesis tests. The package comes with a sample of 500 entries from the General Social Survey (GSS), a long-running survey about American society and opinions. This data is loaded into your environment as `gss`.

The first step in using infer is to pass the data to the `specify()` function to tell `infer` what your dependent and independent variables are. If we are just calculating the mean or proportion of one variable, we just have a dependent variable. For instance, if we wanted to specify the `gss` variable `age` as our response variable, we would type:

```{r}
gss |>
  specify(response = age)
```

By itself this just selects this variable from the `gss` data and prepares it for the next steps.

### Exercises

Now you try to specify `hours` (number of hours worked in week before survey) as the response variable:

```{r gss-hours, exercise = TRUE}

```

```{r gss-hours-solution}
gss |>
  specify(response = hours) 
```

```{r gss-hours-check}
gradethis::grade_this_code()
```

## Submit

```{r context="setup", echo = FALSE}
TPDtutor::submission_ui
```

```{r context="server", echo = FALSE}
TPDtutor::submission_server()
```
